---
title: "ESM 204 - Assignment 4: Technical Appendix"
author: "Jamie Miller"
date: "June 4, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor) # clean_names() for snake_case
library(stargazer) # makes a nice stargazer table for the regression results

```

```{r, include = FALSE}
#Read in the HW4 Data 
HW4 <- read.csv("HW4Data.csv") %>% 
  clean_names()
```

###1. Marginal Cost of Abatement for Each Sector
```{r, echo = FALSE}
# Problem 1: Write down a plausible functional form for the marginal cost of abatement for sector A.
# Use regression analysis to estimate the parameters of that function.

# Use regression to estimate the parameters of the function for Sectors A, B, C, and D 
# Functional Form = y = intercept + slope * X variable + error 

# Coefficients include the following: 
# Intercept: -8.6445 
# Abatement = 0.5768 

mc_a_lm <- lm(mc_a ~ abatement, data = HW4)
#mc_a_lm   # y = 0.5768X - 8.6445 

mc_b_lm <- lm(mc_b ~ abatement, data = HW4)
#mc_b_lm  # y = 0.1987x + 9.3177 

mc_c_lm <- lm(mc_c ~ abatement, data = HW4)
#mc_c_lm  # y = 0.7838x - 11.6550 

mc_d_lm <- lm(mc_d ~ abatement, data = HW4)
#mc_d_lm  # y = 0.2599x + 9.6875
```

```{r, results = 'asis', echo = FALSE}
# Create a stargazer table with summary of regression results

mac_lm_table <- stargazer(mc_a_lm, mc_b_lm, mc_c_lm, mc_d_lm,
                          type = 'html', 
                          #single.row = TRUE,
                          align = TRUE,
                          title = "Table 1. Marginal abatement cost function for each sector.",
                          dep.var.labels = c("A", "B","C","D"), 
                          covariate.labels = c("Abatement", "Constant"),
                          add.lines = list(c("AIC", round(AIC(mc_a_lm),1), round(AIC(mc_b_lm),1), round(AIC(mc_c_lm),1), round(AIC(mc_d_lm),1))))
```

```{r, include = FALSE}
# gather df so graphing is easier
# Marginal Abatement Cost dataframe

mac_df <- gather(HW4, key = "sector", value = "marginal_cost", "mc_a", "mc_b", "mc_c", "mc_d")
#mac_df
```

```{r, echo = FALSE}
# graph it!
# can change line/point colors if we want

cols <- c("mc_a" = "red", "mc_b" = "blue", "mc_c" = "darkgreen", "mc_d" = "orange")
labels <- c("mc_a" = "A", "mc_b" = "B", "mc_c" = "C", "mc_d" = "D")

mac_graph <- ggplot(mac_df, aes(x = abatement, y = marginal_cost)) +
  geom_point(aes(color = sector)) +
  geom_smooth(aes(color = sector), se = FALSE, method = lm) +
#  facet_grid(~sector) +
  scale_color_manual(values = cols,
                     labels = labels,
                     name = "Sector") + 
#  scale_x_continuous(expand = c(0,0)) +
 # scale_y_continuous(expand = c(0,0)) +
  theme_bw() + 
  labs(x = "Carbon Abatement (tons)", y = "Abatement Cost ($/ton)")

mac_graph
```

**Figure 1. Estimated marginal abatement cost functions for each sector.**


###2. Demand curves for carbon emissions
```{r, echo = FALSE}
# current carbon emissions for each sector
# Sectors A, B, and C are in country X. Sector D is in a different country, Y.
# Prices are in $/ton and quantities are in tons

A = 180
B = 200
C = 220
D = 300

# y = mx + b
# y = 0.5768X - 8.6445 

### create function to calculate demand curves
# make and store variables for slope and y-intercept 
slope_a <- mc_a_lm$coefficients[2]
intercept_a <- mc_a_lm$coefficients[1]

slope_b <- mc_b_lm$coefficients[2]
intercept_b <- mc_b_lm$coefficients[1]

slope_c <- mc_c_lm$coefficients[2]
intercept_c <- mc_c_lm$coefficients[1]

slope_d <- mc_d_lm$coefficients[2]
intercept_d <- mc_d_lm$coefficients[1]


# create funtion to calculate new y intercepts. 
# These functions are the equations of the marginal cost of abatement curves for each sector
curve_a <- function(x) {
   slope_a*x + intercept_a
}
curve_b <- function(x) {
   slope_b*x + intercept_b
}
curve_c <- function(x) {
   slope_c*x + intercept_c
}
curve_d <- function(x) {
   slope_d*x + intercept_d
}


# the new y-intercepts (y_intercept_*) for each sector are calculated by plugging in x = current carbon emmisions to the marginal abatement cost functions and solving for y
y_intercept_a <- curve_a(A)
y_intercept_b <- curve_b(B)
y_intercept_c <- curve_c(C)
y_intercept_d <- curve_d(D)


# calculate demand curves for carbon emissions for each sector
# determine new slope by (y0-y1)/(x0-x1) = (0-y_intercept_a)/(A-0)

demand_a = function(x) {
  demand = (-y_intercept_a/A)*x + y_intercept_a
}

demand_b = function(x) {
  demand = (-y_intercept_b/B)*x + y_intercept_b
}

demand_c = function(x) {
  demand = (-y_intercept_c/C)*x + y_intercept_c
}

demand_d = function(x) {
  demand = (-y_intercept_d/D)*x + y_intercept_d
}
```

```{r, echo = FALSE, warning = FALSE}
# Draw demand curves

#cols_2 <- c("demand_a" = "red", "demand_b" = "blue", "demand_c" = "darkgreen", "demand_d" = "orange")
#labels_2 <- c("demand_a" = "A", "demand_b" = "B", "demand_c" = "C", "demand_d" = "D")
# these colors and labels didn't work

# create colors and labels for graph to match figure 1
cols_demand <- c("red", "blue", "darkgreen", "orange")
labels_demand <- c("A", "B", "C", "D")

demand_graph <- ggplot(data.frame(x=c(0,350)), aes(x=x)) + # data.frame gives ggplot something to graph
  stat_function(fun=demand_a, geom = "line", aes(color = "A"), size = 1) +
  stat_function(fun=demand_b, geom = "line", aes(color = "B"), size = 1) +
  stat_function(fun=demand_c, geom = "line", aes(color = "C"), size = 1) +
  stat_function(fun=demand_d, geom = "line", aes(color = "D"), size = 1) +
  scale_y_continuous(limits= c(0,175), expand = c(0,0)) +
  scale_x_continuous(limits= c(0, 300), expand = c(0,0)) +
  scale_color_manual(values = cols_demand,
                     labels = labels_demand,
                     name = "Sector") + 
  theme_bw() + 
  labs(x = "Carbon Abatement (tons)", y = "Abatement Cost ($/ton)")


demand_graph
```

**Figure 2. Carbon demand curves for each sector.**

###3. Country X Policy options
(1) the total cost of meeting the target in country X,
(2) the cost (or benefit) to each sector, and 
(3) the tax revenue generated.

Perhaps create a table to show all the results.

```{r, include = FALSE}
# 3. a) Cap on carbon

################################
# 1. Total cost of meeting target in country X

# reduced carbon emissions for each sector
# Using marginal cost curves
# integrate the area under the marginal abatement cost curves for 0 to 100 tons of carbon abatement
# gives total cost of carbon abatement for 100 tons carbon for each sector
# sum the the total costs for each sector to get the total cost for country X

lossA_cost = integrate(curve_a, 0, 100)
lossB_cost = integrate(curve_b, 0, 100)
lossC_cost = integrate(curve_c, 0, 100)
country_loss_cost = lossA_cost$value + lossB_cost$value + lossC_cost$value  

# The total cost of meeting carbon targets in country X is $6,698.88.

# using demand curves
#lossA = integrate(demand_a, 0, 100)
#lossB = integrate(demand_b, 0, 100)
#lossC = integrate(demand_c, 0, 100)
#country_loss_demand = lossA$value + lossB$value + lossC$value  

# $22,979.05 = total demand. do not use this. this is wrong. so very wrong.


################################
# 2. Total cost for each sector
country_loss_cost_a = lossA_cost$value # $2,019.76
country_loss_cost_b = lossB_cost$value # $1,925.49
country_loss_cost_c = lossC_cost$value # $2,753.63


################################
# 3. Tax revenue generated
# To emit a ton of carbon in country X, you must pay a tax of $t. You will need to find the tax that accomplishes the desired reduction.
# so is there no tax generated on this? Are we supposed to assume a certain tax amount? or is this 3.b)?
```



####Below this point is a work in progress
```{r}
# 3. b) Tax on carbon
#calculating an aggregate supply curve (Sag = MagP + Bag)

Mag =(1/mc_a_lm$coefficients[2])+(1/mc_b_lm$coefficients[2])+(1/mc_c_lm$coefficients[2]) # aggregate slope
Bag = (-(mc_a_lm$coefficients[1]/mc_a_lm$coefficients[2])-(mc_b_lm$coefficients[1]/mc_b_lm$coefficients[2])-(mc_c_lm$coefficients[1]/mc_c_lm$coefficients[2])) # aggregate y-intercept

# Sag = 8.04*P -17

# this function rearranges aggregate supply curve in terms of price
agsupply = function(x) {
  (x - Bag)/Mag
}

#to find the tax, plug in aggregate supply of 300 
taxprice = agsupply(300)
taxprice
# Tax price = $39.42

# to find supply of 
supplyA = function(x){
  (x - mc_a_lm$coefficients[1])/(mc_a_lm$coefficients[2])
  }
supplyB = function(x){
  (x - mc_b_lm$coefficients[1])/(mc_b_lm$coefficients[2])
}
supplyC = function(x){
  (x - mc_c_lm$coefficients[1])/(mc_c_lm$coefficients[2])
}


supplyA(taxprice) # 83.33489
supplyB(taxprice) # 151.4956
supplyC(taxprice) # 65.16953

# Becky and Tara got these same numbers

```


```{r}

```


# 2. Total cost (or benefit) to each sector

```{r}




# 3. Tax revenue generated




```





































