---
title: "ESM 204 - Assignment 4: Technical Appendix"
author: "Jamie Miller"
date: "June 4, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor) # clean_names() for snake_case
library(stargazer) # makes a nice stargazer table for the regression results

```

```{r, include = FALSE}
#Read in the HW4 Data 
HW4 <- read.csv("HW4Data.csv") %>% 
  clean_names()
```

###1. Marginal Cost of Abatement for Each Sector
```{r}
# Problem 1: Write down a plausible functional form for the marginal cost of abatement for sector A.
# Use regression analysis to estimate the parameters of that function.

# Use regression to estimate the parameters of the function for Sectors A, B, C, and D 
# Functional Form = y = intercept + slope * X variable + error 

# Coefficients include the following: 
# Intercept: -8.6445 
# Abatement = 0.5768 

mc_a_lm <- lm(mc_a ~ abatement, data = HW4)
#mc_a_lm   # y = 0.5768X - 8.6445 

mc_b_lm <- lm(mc_b ~ abatement, data = HW4)
#mc_b_lm  # y = 0.1987x + 9.3177 

mc_c_lm <- lm(mc_c ~ abatement, data = HW4)
#mc_c_lm  # y = 0.7838x - 11.6550 

mc_d_lm <- lm(mc_d ~ abatement, data = HW4)
#mc_d_lm  # y = 0.2599x + 9.6875
```

```{r, results = 'asis', echo = FALSE}
# Create a stargazer table with summary of regression results

mac_lm_table <- stargazer(mc_a_lm, mc_b_lm, mc_c_lm, mc_d_lm,
                          type = 'html', 
                          #single.row = TRUE,
                          align = TRUE,
                          title = "Table 1. Marginal abatement cost function for each sector.",
                          dep.var.labels = c("A", "B","C","D"), 
                          covariate.labels = c("Abatement", "Constant"),
                          add.lines = list(c("AIC", round(AIC(mc_a_lm),1), round(AIC(mc_b_lm),1), round(AIC(mc_c_lm),1), round(AIC(mc_d_lm),1))))
```

```{r, include = FALSE}
# gather df so graphing is easier
# Marginal Abatement Cost dataframe

mac_df <- gather(HW4, key = "sector", value = "marginal_cost", "mc_a", "mc_b", "mc_c", "mc_d")
#mac_df
```

```{r, echo = FALSE}
# graph it!
# can change line/point colors if we want

cols <- c("mc_a" = "red", "mc_b" = "blue", "mc_c" = "darkgreen", "mc_d" = "orange")
labels <- c("mc_a" = "A", "mc_b" = "B", "mc_c" = "C", "mc_d" = "D")

mac_graph <- ggplot(mac_df, aes(x = abatement, y = marginal_cost)) +
  geom_point(aes(color = sector)) +
  geom_smooth(aes(color = sector), se = FALSE, method = lm) +
#  facet_grid(~sector) +
  scale_color_manual(values = cols,
                     labels = labels,
                     name = "Sector") + 
#  scale_x_continuous(expand = c(0,0)) +
 # scale_y_continuous(expand = c(0,0)) +
  theme_bw() + 
  labs(x = "Carbon Abatement (tons)", y = "Abatement Cost ($/ton)")

mac_graph
```

**Figure 1. Estimated marginal abatement cost functions for each sector.**


###2. Demand curves for carbon emissions
```{r}
# current carbon emissions for each sector
# Sectors A, B, and C are in country X. Sector D is in a different country, Y.
# Prices are in $/ton and quantities are in tons

A = 180
B = 200
C = 220
D = 300

# y = mx + b
# y = 0.5768X - 8.6445 

### create function to calculate demand curves
# make and store variables for slope and y-intercept 
slope_a <- mc_a_lm$coefficients[2]
intercept_a <- mc_a_lm$coefficients[1]

slope_b <- mc_b_lm$coefficients[2]
intercept_b <- mc_b_lm$coefficients[1]

slope_c <- mc_c_lm$coefficients[2]
intercept_c <- mc_c_lm$coefficients[1]

slope_d <- mc_d_lm$coefficients[2]
intercept_d <- mc_d_lm$coefficients[1]


# create funtion to calculate new y intercepts. 
# These functions are the equations of the marginal cost of abatement curves for each sector
curve_a <- function(x) {
   slope_a*x + intercept_a
}
curve_b <- function(x) {
   slope_b*x + intercept_b
}
curve_c <- function(x) {
   slope_c*x + intercept_c
}
curve_d <- function(x) {
   slope_d*x + intercept_d
}


# the new y-intercepts (y_intercept_*) for each sector are calculated by plugging in x = current carbon emmisions to the marginal abatement cost functions and solving for y
y_intercept_a <- curve_a(A)
y_intercept_b <- curve_b(B)
y_intercept_c <- curve_c(C)
y_intercept_d <- curve_d(D)


# calculate demand curves for carbon emissions for each sector
# determine new slope by (y0-y1)/(x0-x1) = (0-y_intercept_a)/(A-0)

demand_a = function(x) {
  demand = (-y_intercept_a/A)*x + y_intercept_a
}

demand_b = function(x) {
  demand = (-y_intercept_b/B)*x + y_intercept_b
}

demand_c = function(x) {
  demand = (-y_intercept_c/C)*x + y_intercept_c
}

demand_d = function(x) {
  demand = (-y_intercept_d/D)*x + y_intercept_d
}
```

```{r, echo = FALSE, warning = FALSE}
# Draw demand curves

#cols_2 <- c("demand_a" = "red", "demand_b" = "blue", "demand_c" = "darkgreen", "demand_d" = "orange")
#labels_2 <- c("demand_a" = "A", "demand_b" = "B", "demand_c" = "C", "demand_d" = "D")
# these colors and labels didn't work

# create colors and labels for graph to match figure 1
cols_demand <- c("red", "blue", "darkgreen", "orange")
labels_demand <- c("A", "B", "C", "D")

demand_graph <- ggplot(data.frame(x=c(0,350)), aes(x=x)) + # data.frame gives ggplot something to graph
  stat_function(fun=demand_a, geom = "line", aes(color = "A"), size = 1) +
  stat_function(fun=demand_b, geom = "line", aes(color = "B"), size = 1) +
  stat_function(fun=demand_c, geom = "line", aes(color = "C"), size = 1) +
  stat_function(fun=demand_d, geom = "line", aes(color = "D"), size = 1) +
  scale_y_continuous(limits= c(0,175), expand = c(0,0)) +
  scale_x_continuous(limits= c(0, 300), expand = c(0,0)) +
  scale_color_manual(values = cols_demand,
                     labels = labels_demand,
                     name = "Sector") + 
  theme_bw() + 
  labs(x = "Carbon Abatement (tons)", y = "Abatement Cost ($/ton)")


demand_graph
```

**Figure 2. Carbon demand curves for each sector.**

###3. Country X Policy options
(1) the total cost of meeting the target in country X,
(2) the cost (or benefit) to each sector, and 
(3) the tax revenue generated.

Perhaps create a table to show all the results.

a. Cap on carbon. Each sector (A, B, and C) must cut its carbon emissions by 100 tons (thus
reducing total emissions from 600 down to 300).
```{r}
# 3. a) Cap on carbon

################################
# 1. Total cost of meeting target in country X

# reduced carbon emissions for each sector
# Using marginal cost curves
# integrate the area under the marginal abatement cost curves for 0 to 100 tons of carbon abatement
# gives total cost of carbon abatement for 100 tons carbon for each sector
# sum the the total costs for each sector to get the total cost for country X

lossA_cost = integrate(curve_a, 0, A - 100)
lossB_cost = integrate(curve_b, 0, B - 100)
lossC_cost = integrate(curve_c, 0, C - 100)
country_loss_cost = lossA_cost$value + lossB_cost$value + lossC_cost$value  

# The total cost of meeting carbon targets in country X is $7,324.77.

# using demand curves
#lossA = integrate(demand_a, 0, 100)
#lossB = integrate(demand_b, 0, 100)
#lossC = integrate(demand_c, 0, 100)
#country_loss_demand = lossA$value + lossB$value + lossC$value  

# $22,979.05 = total demand. do not use this. this is wrong. so very wrong.


################################
# 2. Total cost for each sector
country_loss_cost_a = lossA_cost$value # $1,154.34
country_loss_cost_b = lossB_cost$value # $1,925.49
country_loss_cost_c = lossC_cost$value # $4,244.95


################################
# 3. Tax revenue generated
# To emit a ton of carbon in country X, you must pay a tax of $t. You will need to find the tax that accomplishes the desired reduction.
# so is there no tax generated on this? Are we supposed to assume a certain tax amount? or is this 3.b)?

# Tax revenue for this option is $0.
```


b. Tax on carbon. To emit a ton of carbon in country X, you must pay a tax of $t. You will need to
find the tax that accomplishes the desired reduction.
```{r}
# 3. b) Tax on carbon
#calculating an aggregate supply curve (Sag = MagP + Bag)

Mag =(1/mc_a_lm$coefficients[2])+(1/mc_b_lm$coefficients[2])+(1/mc_c_lm$coefficients[2]) # aggregate slope
Bag = (-(mc_a_lm$coefficients[1]/mc_a_lm$coefficients[2])-(mc_b_lm$coefficients[1]/mc_b_lm$coefficients[2])-(mc_c_lm$coefficients[1]/mc_c_lm$coefficients[2])) # aggregate y-intercept

# Sag = 8.04*P -17

# this function rearranges aggregate supply curve in terms of price
agsupply = function(x) {
  (x - Bag)/Mag
}

#to find the tax, plug in aggregate supply of 300 
taxprice = agsupply(300)
taxprice
# Tax price = $39.42

# to find supply of 
supplyA = function(x){
  (x - mc_a_lm$coefficients[1])/(mc_a_lm$coefficients[2])
  }
supplyB = function(x){
  (x - mc_b_lm$coefficients[1])/(mc_b_lm$coefficients[2])
}
supplyC = function(x){
  (x - mc_c_lm$coefficients[1])/(mc_c_lm$coefficients[2])
}


supplyA(taxprice) # 83.33489 tons carbon
supplyB(taxprice) # 151.4956 tons carbon
supplyC(taxprice) # 65.16953 tons carbon

supplyTot = supplyA(taxprice) + supplyB(taxprice) +supplyC(taxprice) # Checked that the sum is 300. It is.

# Becky and Tara got similar numbers

```

```{r}
# 3b question:
# 1. Total cost of meeting target in country X

# reduced carbon emissions for each sector
# Using marginal cost curves
# integrate the area under the marginal abatement cost curves for 0 to 100 tons of carbon abatement
# gives total cost of carbon abatement for 100 tons carbon for each sector
# sum the the total costs for each sector to get the total cost for country X

lossA_tax_cost = integrate(curve_a, 0, supplyA(taxprice))
lossB_tax_cost = integrate(curve_b, 0, supplyB(taxprice))
lossC_tax_cost = integrate(curve_c, 0, supplyC(taxprice))
country_loss_tax_cost = lossA_tax_cost$value + lossB_tax_cost$value + lossC_tax_cost$value  

# The total cost of meeting carbon targets in country X is $5,879.81.


################################
# 2. Total cost for each sector
country_loss_tax_cost_a = lossA_tax_cost$value # $1,282.61 Sector A
country_loss_tax_cost_b = lossB_tax_cost$value # $3692.27 Sector B
country_loss_tax_cost_c = lossC_tax_cost$value # $904.93 Sector C


################################
# 3. Tax revenue generated
# To emit a ton of carbon in country X, you must pay a tax of $t. You will need to find the tax that accomplishes the desired reduction.


tax_revenue = taxprice*300
#tax_revenue

# Total tax revenue under this policy is $11,827.97

```



####Below this point is a work in progress

c. Cap and trade. Each sector (A, B, C) is allocated carbon permits equal to their current emissions
minus 100 (same as in (a) above), thus achieving the total reduction of 300. Then, these three
sectors are allowed to trade with each other. You will need to derive the outcome of that
trading.
```{r}

# The Sector abatement is the amount of carbon that each sector abates at the tax price.
# This is the level that they want to abate at so they don't have to pay more than the tax when they are abating carbon.

sectorAabatement = supplyA(taxprice) # 83.3
sectorBabatement = supplyB(taxprice) # 151
sectorCabatement = supplyC(taxprice) # 65.2
#80, 100, 120 

# Integrate under the marginal abatement curve to the supply of carbon at the tax price
lossA_trade = integrate(curve_a, 0, supplyA(taxprice))
lossB_trade = integrate(curve_b, 0, supplyB(taxprice))
lossC_trade = integrate(curve_c, 0, supplyA(taxprice))

# TC_A = A + t*[(180 - 100) - supplyA(taxprice)] 

TC_A = lossA_trade$value + taxprice*((A - 100) - supplyA(taxprice))
TC_A

# 1022.85, so cost is reduced

lossA_trade$value

## Sector B
sectorBabatement*taxprice + lossB_trade$value
## Sector C
sectorCabatement*taxprice + lossC_trade$value






#Cap and trade costs
lossA_t$value + (96.7-80)*
lossB_t$value - (100-48.5)*taxprice
lossC_t$value + (154.8-120)*taxprice



```


```{r}


```






```{r}









```






**From Madeline**
###Part 5
Now assume that every ton of carbon emissions creates 1 ton of local air pollution. Local air pollution
causes economic damages (health, environmental, etc.), but only in the country in which it is emitted.
Assume there are no local air pollution regulations in either country X or country Y.
a. In a carbon cap and trade market that only covers sectors in country X, how much local air
pollution would you expect in country X? In country Y?

#Should 300 in each. 


b. If country Y enters the carbon market for country X (as in question 4 above), how much local
pollution will there be in country X and country Y?

#222.6 tons of carbon in Y, 377.3 tons of carbon in X

c. What advice can you give country X and country Y about the desirability of allowing
international trade of carbon emissions credits?

#From this question it seems that country X would end up emitting lots more carbon with the cap and trade program. There are winners and losers. 





























